---
title: "Rayshader Demo"
author: "Matthew Johns"
date: "4/23/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(rayshader)
```






```{r data-ingest}
#Here, I load a map with the raster package.
#loadzip = tempfile() 
#download.file("https://tylermw.com/data/dem_01.tif.zip", loadzip)
#localtif = raster::raster(unzip(loadzip, "dem_01.tif"))
#unlink(loadzip)

localtif <- raster::raster("dem_01.tif")

```

```{r plot}
#And convert it to a matrix:
elmat = raster_to_matrix(localtif)

#We use another one of rayshader's built-in textures:
elmat %>%
  sphere_shade(texture = "desert") %>%
  plot_map()

#sphere_shade can shift the sun direction:
elmat %>%
  sphere_shade(sunangle = 45, texture = "desert") %>%
  plot_map()

#detect_water and add_water adds a water layer to the map:
elmat %>%
  sphere_shade(texture = "desert") %>%
  add_water(detect_water(elmat), color = "desert") %>%
  plot_map()

#And we can add a raytraced layer from that sun direction as well:
elmat %>%
  sphere_shade(texture = "desert") %>%
  add_water(detect_water(elmat), color = "desert") %>%
  add_shadow(ray_shade(elmat), 0.5) %>%
  plot_map()

#And here we add an ambient occlusion shadow layer, which models 
#lighting from atmospheric scattering:

elmat %>%
  sphere_shade(texture = "desert") %>%
  add_water(detect_water(elmat), color = "desert") %>%
  add_shadow(ray_shade(elmat), 0.5) %>%
  add_shadow(ambient_shade(elmat), 0) %>%
  plot_map()


```

Rayshader also supports 3D mapping by passing a texture map (either external or one produced by rayshader) into the plot_3d function.

```{r}
elmat %>%
  sphere_shade(texture = "desert") %>%
  add_water(detect_water(elmat), color = "desert") %>%
  add_shadow(ray_shade(elmat, zscale = 3), 0.5) %>%
  add_shadow(ambient_shade(elmat), 0) %>%
  plot_3d(elmat, zscale = 10, fov = 0, theta = 135, zoom = 0.75, phi = 45, windowsize = c(1000, 800))
Sys.sleep(0.2)
render_snapshot()
```

You can add a scale bar, as well as a compass using render_scalebar() and render_compass()

```{r}
render_camera(fov = 0, theta = 60, zoom = 0.75, phi = 45)
render_scalebar(limits=c(0, 5, 10),label_unit = "km",position = "W", y=50,
                scale_length = c(0.33,1))
render_compass(position = "E")
render_snapshot(clear=TRUE)
```

You can also render using the built-in pathtracer, powered by rayrender. Simply replace render_snapshot() with render_highquality(). When render_highquality() is called, there’s no need to pre-compute the shadows with any of the _shade() functions, so we remove those:

```{r}
elmat %>%
  sphere_shade(texture = "desert") %>%
  add_water(detect_water(elmat), color = "desert") %>%
  plot_3d(elmat, zscale = 10, fov = 0, theta = 60, zoom = 0.75, phi = 45, windowsize = c(1000, 800))

render_scalebar(limits=c(0, 5, 10),label_unit = "km",position = "W", y=50,
                scale_length = c(0.33,1))

render_compass(position = "E")
Sys.sleep(0.2)
render_highquality(samples=200, scale_text_size = 24,clear=TRUE)
```

You can also easily add a water layer by setting water = TRUE in plot_3d() (and setting waterdepth if the water level is not 0), or by using the function render_water() after the 3D map has been rendered. You can customize the appearance and transparancy of the water layer via function arguments. Here’s an example using bathymetric/topographic data of Monterey Bay, CA (included with rayshader):

```{r}
montshadow = ray_shade(montereybay, zscale = 50, lambert = FALSE)
montamb = ambient_shade(montereybay, zscale = 50)
montereybay %>%
    sphere_shade(zscale = 10, texture = "imhof1") %>%
    add_shadow(montshadow, 0.5) %>%
    add_shadow(montamb, 0) %>%
    plot_3d(montereybay, zscale = 50, fov = 0, theta = -45, phi = 45, 
            windowsize = c(1000, 800), zoom = 0.75,
            water = TRUE, waterdepth = 0, wateralpha = 0.5, watercolor = "lightblue",
            waterlinecolor = "white", waterlinealpha = 0.5)
Sys.sleep(0.2)
render_snapshot(clear=TRUE)
```

Water is also supported in render_highquality(). We load the rayrender package to change the ground material to include a checker pattern. By default, the camera looks at the origin, but we shift it down slightly to center the map.

```{r}
library(rayrender)

montereybay %>%
    sphere_shade(zscale = 10, texture = "imhof1") %>%
    plot_3d(montereybay, zscale = 50, fov = 70, theta = 270, phi = 30, 
            windowsize = c(1000, 800), zoom = 0.6, 
            water = TRUE, waterdepth = 0, wateralpha = 0.5, watercolor = "#233aa1",
            waterlinecolor = "white", waterlinealpha = 0.5)
Sys.sleep(0.2)
render_highquality(lightdirection = c(-45,45), lightaltitude  = 30, clamp_value = 10, 
                   samples = 200, camera_lookat= c(0,-50,0),
                   ground_material = diffuse(color="grey50",checkercolor = "grey20", checkerperiod = 100))
```

Rayshader also has map shapes other than rectangular included c("hex", "circle"), and you can customize the map into any shape you want by setting the areas you do not want to display to NA.

```{r}
par(mfrow = c(1, 2))
montereybay %>% 
    sphere_shade(zscale = 10, texture = "imhof1") %>% 
    add_shadow(montshadow, 0.5) %>%
    add_shadow(montamb, 0) %>%
    plot_3d(montereybay, zscale = 50, fov = 0, theta = -45, phi = 45, windowsize = c(1000, 800), zoom = 0.6,
            water = TRUE, waterdepth = 0, wateralpha = 0.5, watercolor = "lightblue",
            waterlinecolor = "white", waterlinealpha = 0.5, baseshape = "circle")

render_snapshot(clear = TRUE)

montereybay %>% 
    sphere_shade(zscale = 10, texture = "imhof1") %>% 
    add_shadow(montshadow, 0.5) %>%
    add_shadow(montamb, 0) %>%
    plot_3d(montereybay, zscale = 50, fov = 0, theta = -45, phi = 45, windowsize = c(1000, 800), zoom = 0.6,
            water = TRUE, waterdepth = 0, wateralpha = 0.5, watercolor = "lightblue",
            waterlinecolor = "white", waterlinealpha = 0.5, baseshape = "hex")

render_snapshot(clear = TRUE)
```

Adding text labels is done with the render_label() function, which also allows you to customize the line type, color, and size along with the font:

```{r}
montereybay %>% 
    sphere_shade(zscale = 10, texture = "imhof1") %>% 
    add_shadow(montshadow, 0.5) %>%
    add_shadow(montamb,0) %>%
    plot_3d(montereybay, zscale = 50, fov = 0, theta = -100, phi = 30, windowsize = c(1000, 800), zoom = 0.6,
            water = TRUE, waterdepth = 0, waterlinecolor = "white", waterlinealpha = 0.5,
            wateralpha = 0.5, watercolor = "lightblue")
render_label(montereybay, x = 350, y = 160, z = 1000, zscale = 50,
             text = "Moss Landing", textsize = 2, linewidth = 5)
render_label(montereybay, x = 220, y = 70, z = 7000, zscale = 50,
             text = "Santa Cruz", textcolor = "darkred", linecolor = "darkred",
             textsize = 2, linewidth = 5)
render_label(montereybay, x = 300, y = 270, z = 4000, zscale = 50,
             text = "Monterey", dashed = TRUE, textsize = 2, linewidth = 5)
render_label(montereybay, x = 50, y = 270, z = 1000, zscale = 50,  textcolor = "white", linecolor = "white",
             text = "Monterey Canyon", relativez = FALSE, textsize = 2, linewidth = 5) 
Sys.sleep(0.2)
render_snapshot(clear=TRUE)
```

Labels are also supported in render_highquality():

```{r}
render_highquality(samples=200, line_radius = 1, text_size = 18, text_offset = c(0,12,0),
                   clamp_value=10, clear = TRUE)
```

You can also apply a post-processing effect to the 3D maps to render maps with depth of field with the render_depth() function:

```{r}
elmat %>%
  sphere_shade(texture = "desert") %>%
  add_water(detect_water(elmat), color = "desert") %>%
  add_shadow(ray_shade(elmat, zscale = 3), 0.5) %>%
  add_shadow(ambient_shade(elmat), 0) %>%
  plot_3d(elmat, zscale = 10, fov = 30, theta = -225, phi = 25, windowsize = c(1000, 800), zoom = 0.3)
Sys.sleep(0.2)
render_depth(focus = 0.6, focallength = 200, clear = TRUE)
```







